Detecting Photo Manipulation using Reflections on Curved Surfaces

### 2014-02-11 paper/main.tex
added all center point images, work on paper sections 4 and 5

\subsection{Distortion from Perspective Projection}
\label{sec:perspective-distortion}
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.4\textwidth}
                \includegraphics[width=\textwidth]{sphere-perspective-zoom}
                \caption{Perspective view of a sphere}
    \end{subfigure}
    ~
   	\begin{subfigure}[b]{0.4\textwidth}
                \includegraphics[width=\textwidth]{sphere-ortho}
                \caption{Orthographic view of a sphere}
    \end{subfigure}
    \caption{Viewing the sphere with perspective projection introduces noticeable error when solving for the circle projected onto the image plane.}
	\label{sphere-perspective-ortho}
\end{figure}

One issue with this naive approach to finding the center is that perspective projection distorts the shape of the sphere, depending on how centered the sphere is in the camera's view. If the sphere is towards the edge of the camera's view, the extent of the visible part of the sphere towards the edge is closer to the camera than the visible extent of the part of the sphere towards the middle of the image. This causes the sphere to look larger towards the edge of the image and therefore the apparent edge of the circle distorts out towards the edge of the image. As a result, the outline projected onto the image is slightly elliptical, as in Figure~\ref{sphere-perspective-ortho}.

@@

\chapter{Results}
As detailed in Section~\ref{sec:perspective-distortion}, it as not as simple as finding the outline of a perfect circle to find the projection of the center of the sphere in the image. Therefore, for the purpose of testing the method, test images were generated with a small sphere located at the exact center of the reflective sphere made slightly transparent.

@@

\section{Typical Results for Genuine Images}
% typical results for untampered images- how many pixels away from the center, how scattered the intersections can be
% address: effects of higher resolution, edited images: shifts forward/back, side to side, farther back, composite,
% why the radius test breaks for certain adjustments

>>>>

\subsection{Distortion from Perspective Projection}
\label{sec:perspective-distortion}

\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{sphere-distortion}
	\caption{If the image plane is not facing the sphere head-on, the distance from the point $P_1$ to its projection $p_1$ through the center of projection $C$ is shorter than the distance from $P_2$ to $p_2$, so one side is distorted. Additonally, the projection $q$ of the sphere center $Q$ is not the midpoint of $p_1$ and $p_2$.}
	\label{sphere-distortion}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.4\textwidth}
                \includegraphics[width=\textwidth]{sphere-perspective-zoom}
                \caption{Perspective view of a sphere}
    \end{subfigure}
    ~
   	\begin{subfigure}[b]{0.4\textwidth}
                \includegraphics[width=\textwidth]{sphere-ortho}
                \caption{Orthographic view of a sphere}
    \end{subfigure}
    \caption{Viewing the sphere with perspective projection introduces noticeable error when solving for the circle projected onto the image plane.}
	\label{sphere-perspective-ortho}
\end{figure}

One issue with this naive approach to finding the center is that perspective projection distorts the shape of the sphere, depending on how centered the sphere is in the camera's view. If the sphere is towards the edge of the camera's view, the extent of the visible part of the sphere towards the edge is closer to the camera than the visible extent of the part of the sphere towards the middle of the image. This causes the sphere to look larger towards the edge of the image and therefore the apparent edge of the circle distorts out towards the edge of the image. This effect is described in Figure~\ref{sphere-distortion}. As a result, the outline projected onto the image is slightly elliptical, as in Figure~\ref{sphere-perspective-ortho}.

@@

\chapter{Results}
\begin{figure}
	\centering
    	\includegraphics[width=0.8\textwidth]{center-error}
	\caption{The center found when finding the best fit for a perfect circle (green cross) is significantly offset from the actual projected center of the sphere (pink dot).}
	\label{center-error}
\end{figure}

As detailed in Section~\ref{sec:perspective-distortion}, it as not as simple as finding the outline of a perfect circle to find the projection of the center of the sphere in the image. Therefore, for the purpose of testing the method, test images were generated with a small sphere located at the exact center of the reflective sphere made slightly transparent. Figure~\ref{center-error} shows how inaccurate the naive center-finding method can be.

@@

% TODO measurable error- residuals?

\section{Typical Results for Genuine Images}
% typical results for untampered images- how many pixels away from the center, how scattered the intersections can be
% effects of higher resolution
\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{1b-genuine}
	\caption{The chair and the cube are reasonably consistent with the center of the sphere, but the incident rays from the letters appear to intersect at a point slightly offset from the center, despite being unmanipulated.}
	\label{1b-genuine}
\end{figure}
Based on images containing relatively large and relatively small reflective spheres with objects at varying distances, the projections of the incident rays usually come within 5 pixels of the sphere center. This increases with higher resolution images. As seen in Figure~\ref{1b-genuine}, some objects seem to have a clean intersection point that is offset from the sphere center. The source of this error is unknown.

\section{Effects of Forgery}

% address: edited images: shifts forward/back, side to side, farther back, composite,
% why the radius test breaks for certain adjustments
